The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md
Update manuscript.Rmd

Sociality exists across scales (Whitehead 2008). For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group (Franks et al. 2010). Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges. In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (Farine et al. 2015).

@@

  1) How do social phenotypes across scales differently influence fitness? Are some social scales better predictors for different fitness metrics?

>>>>

Sociality exists across scales (Whitehead 2008). For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group (Franks et al. 2010). Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges. In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (see Glossary; Farine et al. 2015).

@@

  1) How do social phenotypes across scales differently influence fitness? Are some temporal or social scales better predictors for different fitness metrics?
